### 2021-08-28 manuscript/methodology.tex
methodology.tex: Revisei duas subsections da metodologia que foram: The total-field anomaly e Equivalent layer for magnetic data

Let $(x_i, y_i, z_i), i =  1,2,3,...N$, be a observed dataset in a region considering a right-handed Cartesian coordinate system with the $x$-axis pointing north, $y$-axis pointing east and $z$-axis pointing downward. The total-field anomaly at the $i$th observation can be approximated to:
\begin{equation}
	\Delta T(x_i, y_i, z_i) = \hat{\mathbf{F}}^{\top} \mathbf{B}(x_i, y_i, z_i) \: ,
	\label{eq:tfanomaly}
\end{equation}
where, $\mathbf{B}(x_i, y_i, z_i)$ is the crustal field, $\hat{\mathbf{F}}^{\top}$ is the transposed unitary vector with the main field directions, with $\hat{\mathbf{F}}$ described as:
\begin{equation}
	\hat{\mathbf{F}} = \left[
	\begin{array}{c}
		F_x \\
		F_y \\
		F_z
	\end{array} \right] = 
	\left[
	\begin{array}{c}
		\cos(I_{0}) \, \cos(D_{0}) \\
		\cos(I_{0}) \, \sin(D_{0}) \\
		\sin(I_{0})
	\end{array} \right],
	\label{eq:unit_vector_F}
\end{equation}
where $I_{0}$ is the inclination and $D_{0}$ the declination of the main field, respectively.

Considering a uniform magnetized body with volume $v$ and a total magnetization vector $\mathbf{m}$, the induced magnetic field is:
\begin{equation}
	\mathbf{B}(x_i, y_i, z_i) = c_{m} \, \frac{\mu_{0}}{4\pi} \: \mathbf{M}(x_i, y_i, z_i) \: 
	\mathbf{m} \: ,
	\label{eq:induction-general}
\end{equation}
where, $\mu_{0} = 4\pi \, 10^{-7}$ H/m is the magnetic constant, 
$c_{m} = 10^{9}$ is a constant that transforms the induced magnetic field from Tesla (T) to nanotesla (nT) and 
$\mathbf{M}(x_i, y_i, z_i)$ is a $3 \times 3$ matrix given by:
\begin{equation}
	\mathbf{M}(x_i, y_i, z_i) =
	\left[
	\begin{array}{ccc}
		\partial_{xx} \phi(x_i,y_i,z_i) & \partial_{xy} \phi(x_i,y_i,z_i) & 
		\partial_{xz} \phi(x_i,y_i,z_i) \\
		\partial_{xy} \phi(x_i,y_i,z_i) & \partial_{yy} \phi(x_i,y_i,z_i) & 
		\partial_{yz} \phi(x_i,y_i,z_i) \\
		\partial_{xz} \phi(x_i,y_i,z_i) & \partial_{yz} \phi(x_i,y_i,z_i) & 
		\partial_{zz} \phi(x_i,y_i,z_i)
	\end{array}
	\right] \: ,
	\label{eq:M}
\end{equation}
where, $\partial_{\alpha\beta} \phi(x_i,y_i,z_i)$ with $\alpha = x, y, z$ and 
$\beta = x, y, z$, are the second derivatives of the function $\phi(x_i,y_i,z_i)$
with respect to $x$, $y$ and $z$:

\begin{equation}
	\phi(x_i,y_i,z_i) = \int\int\limits_{v}\int \frac{1}{r} \: dv,
	\label{eq:phi}
\end{equation}
where the function $\dfrac{1}{r}$ is given by:

\begin{equation}
	\dfrac{1}{\sqrt{(x_i - x_j)^{2} + 
			(y_i - y_j)^{2} + (z_i - z_j)^{2}}} \,
	\label{eq:r}
\end{equation}
and $x_j, y_j, z_j$ are the $j$th Cartesian coordinates within the volume elements of the magnetized body with volume $v$, where the integral (equation \ref{eq:phi}) is conducted.

@@

Grounded on the equivalent layer principle it is possible to calculate the total-field anomaly $\Delta T(x_i, y_i, z_i)$ (equation \ref{eq:tfanomaly-general}) with the convolution between the harmonic function and the physical property:
\begin{equation}
\Delta T(x_{i}, y_{i}, z_{i})
= \int \limits_{-\infty}^{+\infty}
\int \limits_{-\infty}^{+\infty}
p(x_j, y_j, z_{c}) \,
\left[ c_{m} \, \frac{\mu_{0}}{4\pi} \,
\hat{\mathbf{F}}^{\top} \mathbf{H} \, 
\hat{\mathbf{h}} \right] \,
dx \, dy \: ,
\label{eq:tf-p-continuous-mag-positive}
\end{equation}
where $z_c$ is a constant representing the depth of the equivalent layer with $z_i < z_c$. The unitary vector $\hat{\mathbf{h}}$ is the magnetization directions of the equivalent sources over the layer:
\begin{equation}
\hat{\mathbf{h}} = \left[
\begin{array}{c}
{h}_x \\
{h}_y \\
{h}_z
\end{array} \right] = 
 \left[
\begin{array}{c}
\cos(I) \, \cos(D) \\
\cos(I) \, \sin(D) \\
\sin(I)
\end{array}
\right] \: ,
\label{eq:h_hat}
\end{equation}
where $I$ and $D$ are, respectively, the inclination and declination of the equivalent sources, $\mathbf{H}$ is a $3 \times 3$ matrix that contains the second derivatives in relation to the observed Cartesian coordinates $x, y, z$ as presented in equation \ref{eq:r}:
\begin{equation}
\mathbf{H} =
\left[
\begin{array}{ccc}
\partial_{xx} \frac{1}{r} & 
\partial_{xy} \frac{1}{r} & 
\partial_{xz} \frac{1}{r} \\
\partial_{xy} \frac{1}{r} & 
\partial_{yy} \frac{1}{r} & 
\partial_{yz} \frac{1}{r} \\
\partial_{xz} \frac{1}{r} & 
\partial_{yz} \frac{1}{r} & 
\partial_{zz} \frac{1}{r}
\end{array}
\right] \: =
\left[
\begin{array}{ccc}
H_{xx} & 
H_{xy} & 
H_{xz} \\
H_{xy} & 
H_{yy} & 
H_{yz} \\
H_{xz} & 
H_{yz} & 
H_{zz}
\end{array}
\right] \: ,
\label{eq:Hi}
\end{equation}
and the physical property $p(x_j, y_j, z_{c})$ represents the magnetic dipole moment distribution over the layer and has unit of $Am^2$.

Discretizing equation \ref{eq:tf-p-continuous-mag-positive} we get:
\begin{equation}
\Delta T(x_{i}, y_{i}, z_{i}) = \sum_{j=1}^{M} p_j a_{ij}\: ,
\label{eq:integral-sum_mag}
\end{equation}
where $j = 1,2,3,...,M$ are the equivalent sources discretized and distributed across the layer and $a_{ij}$ is given by:
\begin{equation}
a_{ij}
= c_{m} \, \frac{\mu_{0}}{4\pi} \, \hat{\mathbf{F}}^{\top} \mathbf{H}_{ij} \: \hat{\mathbf{h}} \: .
\label{eq:aij_mag}
\end{equation}
Equation \ref{eq:integral-sum_mag} can be written as:
\begin{equation}
\mathbf{d}(\mathbf{p}) = \mathbf{A} \mathbf{p} \: ,
\label{eq:predicted-data-vector_mag}
\end{equation}
where $\mathbf{d}(\mathbf{p})$ is the vector of total-field anomaly, $\mathbf{A}$ is a matrix containing the elements given by equation \ref{eq:aij_mag}, also known as the sensitivity matrix and $\mathbf{p}$ is the vector containing the dipole moments of each equivalent source. By using the normal equations:
\begin{equation}
	\mathbf{A}^{\top}\mathbf{A}{\mathbf{p}} = 
	\mathbf{A}^{\top} \mathbf{d}^{o} \:
	\label{eq:normal-equations}
\end{equation} 
which is a conventional manner of solving linear systems, the estimative of the dipole moment parameters vector can be calculated from the total-field anomaly as:
\begin{equation}
\hat{\mathbf{p}} = \left( \mathbf{A}^{\top}\mathbf{A} %+ 
%\mu \, \mathbf{I} 
\right)^{-1}
\mathbf{A}^{\top} \mathbf{d}^{o} \:
\label{eq:estimated-p-parameter-space}
\end{equation}
where $\mathbf{d}^{o}$ is the observed total-field anomaly. Equation \ref{eq:estimated-p-parameter-space} will be referenced throughout this work as the classical method for solving the equivalent layer.

>>>>

Let $\Delta T(x_i, y_i, z_i), i =  1,...,N$, be a observed dataset in a region considering a right-handed Cartesian coordinate system with the $x$-axis pointing north, $y$-axis pointing east and $z$-axis pointing downward. The total-field anomaly at the $i$th observation can be approximated to:
\begin{equation}
	\Delta T(x_i, y_i, z_i) = \hat{\mathbf{F}}^{\top} \mathbf{B}(x_i, y_i, z_i) \: ,
	\label{eq:tfanomaly}
\end{equation}
where, $\mathbf{B}(x_i, y_i, z_i)$ is the crustal field, $\hat{\mathbf{F}}^{\top}$ is the transposed unitary vector with the main field directions, with $\hat{\mathbf{F}}$ described as:
\begin{equation}
	\hat{\mathbf{F}} = \left[
	\begin{array}{c}
		F_x \\
		F_y \\
		F_z
	\end{array} \right] = 
	\left[
	\begin{array}{c}
		\cos(I_{0}) \, \cos(D_{0}) \\
		\cos(I_{0}) \, \sin(D_{0}) \\
		\sin(I_{0})
	\end{array} \right],
	\label{eq:unit_vector_F}
\end{equation}
where $I_{0}$ is the inclination and $D_{0}$ the declination of the main field, respectively.

Considering a uniform magnetized body with volume $v$ and a total magnetization vector $\mathbf{m}$, the induced magnetic field at the $i$th observation is:
\begin{equation}
	\mathbf{B}(x_i, y_i, z_i) = c_{m} \, \frac{\mu_{0}}{4\pi} \: \mathbf{M}(x_i, y_i, z_i) \: 
	\mathbf{m} \: ,
	\label{eq:induction-general}
\end{equation}
where, $\mu_{0} = 4\pi \, 10^{-7}$ H/m is the magnetic constant, 
$c_{m} = 10^{9}$ is a constant that transforms the induced magnetic field from Tesla (T) to nanotesla (nT) and 
$\mathbf{M}(x_i, y_i, z_i)$ is a $3 \times 3$ matrix given by:
\begin{equation}
	\mathbf{M}(x_i, y_i, z_i) =
	\left[
	\begin{array}{ccc}
		\partial_{xx} \phi(x_i,y_i,z_i) & \partial_{xy} \phi(x_i,y_i,z_i) & 
		\partial_{xz} \phi(x_i,y_i,z_i) \\
		\partial_{xy} \phi(x_i,y_i,z_i) & \partial_{yy} \phi(x_i,y_i,z_i) & 
		\partial_{yz} \phi(x_i,y_i,z_i) \\
		\partial_{xz} \phi(x_i,y_i,z_i) & \partial_{yz} \phi(x_i,y_i,z_i) & 
		\partial_{zz} \phi(x_i,y_i,z_i)
	\end{array}
	\right] \: ,
	\label{eq:M}
\end{equation}
where, $\partial_{\alpha\beta} \phi(x_i,y_i,z_i)$ with $\alpha = x, y, z$ and 
$\beta = x, y, z$, are the second derivatives of the function $\phi(x_i,y_i,z_i)$
with respect to $x$, $y$ and $z$:

\begin{equation}
	\phi(x_i,y_i,z_i) = \int\int\limits_{v}\int \frac{1}{r} \: dv,
	\label{eq:phi}
\end{equation}
where

\begin{equation}
	\dfrac{1}{r} = \dfrac{1}{\sqrt{(x_i - x_j)^{2} + 
			(y_i - y_j)^{2} + (z_i - z_j)^{2}}} \,
	\label{eq:r}
\end{equation}
and $x_j, y_j, z_j$ are the $j$th Cartesian coordinates within the volume element of the magnetized body with volume $v$, where the integral (equation \ref{eq:phi}) is conducted.

@@

Grounded on the equivalent layer principle it is possible to calculate the total-field anomaly $\Delta T(x_i, y_i, z_i)$ (equation \ref{eq:tfanomaly-general}) with the convolution between the harmonic function and the physical property:
\begin{equation}
\Delta T(x_{i}, y_{i}, z_{i})
= \int \limits_{-\infty}^{+\infty}
\int \limits_{-\infty}^{+\infty}
p(x_j, y_j, z_{c}) \,
\left[ c_{m} \, \frac{\mu_{0}}{4\pi} \,
\hat{\mathbf{F}}^{\top} \mathbf{H} \, 
\hat{\mathbf{h}} \right] \,
dx \, dy \: ,
\label{eq:tf-p-continuous-mag-positive}
\end{equation}
where $z_c$ is a constant representing the depth of the equivalent layer with $z_i < z_c$. The unitary vector $\hat{\mathbf{h}}$ is the magnetization directions of the equivalent sources over the layer:
\begin{equation}
\hat{\mathbf{h}} = \left[
\begin{array}{c}
{h}_x \\
{h}_y \\
{h}_z
\end{array} \right] = 
 \left[
\begin{array}{c}
\cos(I) \, \cos(D) \\
\cos(I) \, \sin(D) \\
\sin(I)
\end{array}
\right] \: ,
\label{eq:h_hat}
\end{equation}
where $I$ and $D$ are, respectively, the inclination and declination of the equivalent sources, $\mathbf{H}$ is a $3 \times 3$ matrix that contains the second derivatives in relation to the observed Cartesian coordinates $x, y, z$ as presented in equation \ref{eq:r}:
\begin{equation}
\mathbf{H} =
\left[
\begin{array}{ccc}
\partial_{xx} \frac{1}{r} & 
\partial_{xy} \frac{1}{r} & 
\partial_{xz} \frac{1}{r} \\
\partial_{xy} \frac{1}{r} & 
\partial_{yy} \frac{1}{r} & 
\partial_{yz} \frac{1}{r} \\
\partial_{xz} \frac{1}{r} & 
\partial_{yz} \frac{1}{r} & 
\partial_{zz} \frac{1}{r}
\end{array}
\right] \: =
\left[
\begin{array}{ccc}
H_{xx} & 
H_{xy} & 
H_{xz} \\
H_{xy} & 
H_{yy} & 
H_{yz} \\
H_{xz} & 
H_{yz} & 
H_{zz}
\end{array}
\right] \: ,
\label{eq:Hi}
\end{equation}
and the physical property $p(x_j, y_j, z_{c})$ represents the $j$th magnetic dipole moment (in $Am^2$) produced by the $j$th dipole locate over the equivalent layer at the $j$th Cartesian coordinates 
$(x_j, y_j, z_{c})$.

Discretizing equation \ref{eq:tf-p-continuous-mag-positive} we get:
\begin{equation}
\Delta T(x_{i}, y_{i}, z_{i}) = \sum_{j=1}^{M} p_j a_{ij}\: ,
\label{eq:integral-sum_mag}
\end{equation}
where the subscript $j$ denotes a discrete equivalent source, totaling $M$ equivalent sources 
that are distributed over the layer and $a_{ij}$ is given by:
\begin{equation}
a_{ij}
= c_{m} \, \frac{\mu_{0}}{4\pi} \, \hat{\mathbf{F}}^{\top} \mathbf{H}_{ij} \: \hat{\mathbf{h}} \: .
\label{eq:aij_mag}
\end{equation}
Equation \ref{eq:integral-sum_mag} can be written in matrix notation as:
\begin{equation}
\mathbf{d}(\mathbf{p}) = \mathbf{A} \mathbf{p} \: ,
\label{eq:predicted-data-vector_mag}
\end{equation}
where $\mathbf{d}(\mathbf{p})$ is the $N-$dimensional vector of total-field anomaly 
$(\Delta T(x_i, y_i, z_i), i =  1,...,N)$, $\mathbf{A}$ is a matrix containing the elements given by equation \ref{eq:aij_mag}, also known as the sensitivity matrix and $\mathbf{p}$ is the vector containing the dipole moments of each equivalent source.

Let $\mathbf{d}^{o}$ be an $N-$dimensional vector that contains the observed total-field anomaly.
By solving the least-squares normal equation associated with equation \ref{eq:predicted-data-vector_mag}, 
we get
\begin{equation}
	\mathbf{A}^{\top}\mathbf{A}{\mathbf{p}} = 
	\mathbf{A}^{\top} \mathbf{d}^{o} \: ,
	\label{eq:normal-equations}
\end{equation} 
and we estimate the parameter vector that contains the unknown dipole moments over the equivalent layer, i.e.,
\begin{equation}
\hat{\mathbf{p}} = \left( \mathbf{A}^{\top}\mathbf{A} %+ 
%\mu \, \mathbf{I} 
\right)^{-1}
\mathbf{A}^{\top} \mathbf{d}^{o} \:
\label{eq:estimated-p-parameter-space}
\end{equation}

Equation \ref{eq:estimated-p-parameter-space} will be referenced throughout this work as the classical method for solving the equivalent layer.
